What covert verbal actions tell us about the interplay between language, action, and perception

### 2021-04-14 manuscript.tex
minor updates to fig1

The ability to examine our private thoughts is central to our subjective experience... Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...

Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...

Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery...

In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions... We explore two main themes. First, how is produced... Second... by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
\end{center}
\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option... FIGURE IN PROGRESS.}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition. The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}

>>>>

The ability to mentally examine our thoughts is central to our subjective experience. Silently rehearsing... allows us to become better at performing them \cite{}, to explore novel situations \cite{}, or to... Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...

% One of the most influential theoretical model of this broad phenomenon, the motor simulation theory (Jeannerod, 2006, 1994, 2001), contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017). A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models). Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987). The function of internal models is to estimate and anticipate the outcome of a motor command. Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states (Gentsch et al., 2016; L\oe venbruck et al., 2018). Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...

Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}... By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as “multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals” (L\oe venbruck et al., 2018). In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004). This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017).

In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions. We explore two main themes. First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions. Second... by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some novel and possibly fruitful lines of research.

@@

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
\end{center}
\caption{General depiction of the balance (weighing) between the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option... FIGURE IN PROGRESS.}\label{fig:1}
\end{figure}

\begin{figure}[ht] % float was h! initially
\begin{center}
\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
\end{center}
\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition during motor imagery. The cerebral complex formed by the preSMA, the rIFC, and the STN is known as the \textit{inhibitory triangle} may be responsible for braking motor commands during covert speech production... FIGURE IN PROGRESS.}\label{fig:2}
\end{figure}
